Portal Forecast

### 2018-02-14 index.Rmd
add heading for most abundance species plots

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions)
plot(sp_predict)
```
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)

>>>>

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions)
plot(sp_predict)
```

## Most Abundant Species

```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)
